Code Publishing Tutorial

### 2025-01-25 index.qmd
Major rewrite
First explain copyright and licenses,
then practice citation and attribution,
then choose own license.

Create file `copyright.qmd` with material
from `choose_license.qmd` and with
additional information on license conditions
and providing attribution.

Create files `data.qmd` and `code.qmd` with
material from `setup.qmd`. Immediately
cover the citation and attribution.

Relicense `Manuscript.qmd` and all code chunks under CC0 1.0. Relicense other
materials under CC BY-SA 4.0.
Various minor improvements

In particular, we will assume you have installed [Git](https://git-scm.com/downloads), [R](https://cloud.r-project.org/), [RStudio](https://posit.co/download/rstudio-desktop/), and [Quarto](https://quarto.org/docs/download/). Windows users may additionally need [RTools](https://cloud.r-project.org/bin/windows/Rtools/).

@@

[Get started](intro.qmd){.btn-action-primary .btn-action .btn .btn-success .btn-lg}

>>>>

In particular, we will assume you have installed [Git](https://git-scm.com/downloads), [R](https://cloud.r-project.org/), [RStudio](https://posit.co/download/rstudio-desktop/#:~:text=2%3A%20Install%20RStudio), and [Quarto](https://quarto.org/docs/download/). Windows users may additionally need [RTools](https://cloud.r-project.org/bin/windows/Rtools/).

@@

[Get started](intro.qmd){.btn .btn-lg .btn-success}
